Toward Resolved Simulations of Burning Fronts in Thermonuclear X-ray Bursts

### 2018-12-31 astronum_2018/astronum-xrb.tex
fix ref
refix the caption

Figure~\ref{fig:xrb} shows the flame structure for an initial 2D run
at 0.007~s.  Vertical profiles at a few radial distances from the
origin are shown for the same quantities in
Figure~\ref{fig:xrb-profiles}.  The burning layer is only about 10~m
high.  Underneath is \isot{Ni}{56}, representative of the underlying
neutron star, and above it is a very low density ($10^{-4}~\gcc$)
buffer.  Only a portion of the vertical extent is shown.  The top
panel shows the temperature structure.  The initial perturbation
reached to $2\times 10^4~\mathrm{cm}$, so at this point, the extent of
the burnt region has nearly doubled.  The flame structure is quite
wide, since there are multiple burning stages beyond just helium to
carbon, and this shows up in the composition.  This is seen more
clearly in the next panel which shows the mean molecular weight of the
nuclei ($\bar{A}$).  We see that the further behind the head of the
flame we are, the heavier the ash nuclei.  We also see the head of the
flame appears lifted off of the base of the burning layer---unburned
material underlies the spreading flame.  This is reminiscent of the
flame structure seen in the earlier simulations of
\cite{cavecchi:2012}.  The third panel shows the energy generation
rate.  It is strongest just above the neutron star surface, behind the
flame.  We again see that the head of the flame is detached from the
base of the atmosphere, with the strongest burning at the head of the
flame slightly higher up in the atmosphere.  Finally, the bottom panel
shows the velocity through the plane of the simulation---this is
induced by the Coriolis force as the burning fluid expands and begins
to spread laterally.  A tight hurricane structure has setup as a
result of the flame spreading.  This is the geostrophic balance
discussed in \cite{SPIT_ETAL02}.  These calculations are ongoing and
will be the subject of a detailed study in the near future.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{xrb_profiles}
\caption{\label{fig:xrb_profiles} Vertical profiles at several laterial distances
  from the vertical axis through the plots shown in Figure~\ref{fig:xrb}.  These
  profiles sample the region behind and ahead of the flame.}
\end{figure}

>>>>

Figure~\ref{fig:xrb} shows the flame structure for an initial 2D run
at 0.007~s.  Vertical profiles at a few radial distances from the
origin are shown for the same quantities in
Figure~\ref{fig:xrb_profiles}.  The burning layer is only about 10~m
high.  Underneath is \isot{Ni}{56}, representative of the underlying
neutron star, and above it is a very low density ($10^{-4}~\gcc$)
buffer.  Only a portion of the vertical extent is shown.  The top
panel shows the temperature structure.  The initial perturbation
reached to $2\times 10^4~\mathrm{cm}$, so at this point, the extent of
the burnt region has nearly doubled.  The flame structure is quite
wide, since there are multiple burning stages beyond just helium to
carbon, and this shows up in the composition.  This is seen more
clearly in the next panel which shows the mean molecular weight of the
nuclei ($\bar{A}$).  We see that the further behind the head of the
flame we are, the heavier the ash nuclei.  We also see the head of the
flame appears lifted off of the base of the burning layer---unburned
material underlies the spreading flame.  This is reminiscent of the
flame structure seen in the earlier simulations of
\cite{cavecchi:2012}.  The third panel shows the energy generation
rate.  It is strongest just above the neutron star surface, behind the
flame.  We again see that the head of the flame is detached from the
base of the atmosphere, with the strongest burning at the head of the
flame slightly higher up in the atmosphere.  Finally, the bottom panel
shows the velocity through the plane of the simulation---this is
induced by the Coriolis force as the burning fluid expands and begins
to spread laterally.  A tight hurricane structure has setup as a
result of the flame spreading.  This is the geostrophic balance
discussed in \cite{SPIT_ETAL02}.  These calculations are ongoing and
will be the subject of a detailed study in the near future.

@@

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{xrb_profiles}
\caption{\label{fig:xrb_profiles} Vertical profiles at several radial distances
  from the vertical axis through the plots shown in Figure~\ref{fig:xrb}.  These
  profiles sample the region behind and ahead of the flame.}
\end{figure}
